

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).


Dataframe and Lists
```{r}
str(mtcars)



```

```{r}
head(mtcars)
tail(mtcars)
```


1. Defining our own DATAFRAME
```{r}
# Definition of vectors
name <- c("Mercury", "Venus", "Earth", "Mars", "Jupiter", "Saturn", "Uranus", "Neptune")
type <- c("Terrestrial planet", "Terrestrial planet", "Terrestrial planet", 
          "Terrestrial planet", "Gas giant", "Gas giant", "Gas giant", "Gas giant")
diameter <- c(0.382, 0.949, 1, 0.532, 11.209, 9.449, 4.007, 3.883)
rotation <- c(58.64, -243.02, 1, 1.03, 0.41, 0.43, -0.72, 0.67)
rings <- c(FALSE, FALSE, FALSE, FALSE, TRUE, TRUE, TRUE, TRUE)

# Create a data frame from the vectors
planets_df <-data.frame(name, type, diameter, rotation, rings)
str(planets_df)

```



2. Instead of using numerics to select elements of a data frame, you can also use the variable names to select columns of a data frame.
```{r}
planets_df[1:3,"diameter"]

# Select the rings variable from planets_df
rings_vector <- planets_df$rings
rings_vector

# code to select all columns for planets with rings(Another way of subsetting)
planets_df[rings_vector,] 



```


3. SUBSETTING THE DATAFRAME
The first argument of subset() specifies the data set for which you want a subset. By adding the second argument, you give R the necessary information and conditions to select the correct subset.

```{r}
# Select planets with diameter < 1
subset(planets_df,subset = diameter < 1 )
```

